---
title: "Juvenile salmon migration report: northern Strait of Georgia to Johnstone Strait 2017"
output:
  rmarkdown::pdf_document:
    
    fig_caption: yes
    includes:
      in_header: figure_opts.tex
    latex_engine: xelatex
sansfont: Times New Roman
fontsize: 12pt

header-includes:
- \usepackage{booktabs}
- \usepackage{sectsty} \sectionfont{\centering \emph}
      
---

\begin{center}
\large
— Hakai Institute Juvenile Salmon Program —
\end{center}

```{r, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(tidyverse)
library(forcats)
library(lubridate)
library(ggjoy)
library(knitr)
# Un comment code below to get up to date catch and sea lice data.
#source(file = "./raw_scripts/pre-process.R")

theme_set(theme_classic(base_size = 12) +
  theme(text = element_text(family = "Times")))

field_2017 <- read_csv("./processed_data/field_2017.csv")
sea_lice_2017 <- read_csv("./processed_data/sea_lice_2017.csv")
# Need to manually update raw data files to get pre processed before these files will
# display up to date data
ysi_data <- read_csv("./processed_data/ysi_data.csv")
chl_a_data <- read_csv("./processed_data/chl_a_data.csv")
js_ctd <- read_csv("./processed_data/js_ctd.csv")
di_ctd <- read_csv("./processed_data/di_ctd.csv")
```


## Aim 

To provide regular in-season summaries of juvenile Fraser salmon migration catch statistics, health indices, and oceanographic conditions in the northern Strait of Georgia to Johnstone Strait region. 

## Background

The Hakai Institute Juvenile Salmon Program was launched in the spring of 2015 in a collaborative partnership with UBC, SFU, Salmon Coast, Pacific Salmon Foundation, and DFO. The program operates in the Discovery Islands and Johnstone Strait (Figure 1) and thus provides information on the health of juvenile Fraser River salmon after passage through: 

1) Strait of Georgia – stratified high plankton biomass zone; and 

2) Discovery Islands & Johnstone Strait – highly-mixed low-plankton-biomass zone, and area of high wild-farmed fish interactions.

## Program Objectives

1) Determine migration timing and pathways; 

2) Migration habitat mapping - oceanographic conditions along the migration route;

3) Understand the dynamics of the plankton food-webs that underpin juvenile salmon growth and
health;

4) Understand parasite and pathogen infection dynamics and their impact on juvenile salmon growth and
health.

## Key Parameters Reported
* Catch Statistics
* Parasite Loads
* Sockeye Length and Weight
* Oceanographic Conditions

![Salmon sampling locations in the Discovery Islands and Johnstone Strait in 2017 (yellow circles).](./final_figures/map_2017.pdf)

The following plots are subject to change as the underlying data are preliminary and subject to further quality assurance. 

We are endeavouring to provide useful information for the entire salmon research community. As such we welcome any feedback. Please direct questions or comments to Brian Hunt (B.Hunt@oceans.ubc.ca) and/or Brett Johnson (Brett.Johnson@hakai.org). 

__Report prepared by:__ Brett Johnson, Carly Janusson, Julian Gan, and Brian Hunt  
__Updated:__ `r Sys.Date()`  

## Catch Statistics
### Cumulative Abundance of all Species
```{r All Species Cumulative Abundance, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "The cumulative abundance of fish captured in the Discovery Islands and Johnstone Strait in 2017."}
# This calculates cumulative abundance, regardless of region



cum_abund <- field_2017 %>%
                filter(!survey.id %in% c("DE457","DE458","DE459","DE460","DE461","DE462","DE463","DE464")) %>% 
                        # The line above removes Sam James's MSc seines from this analysis becuse they are outside the 
                        # standardized effort required for cumulative abundance analysis to be unbiased. 
                select(region, date, so.total, pi.total, cu.total, co.total, he.total, ck.total) %>%
                replace(is.na(.),0) %>% 
                #na.omit() %>% 
                group_by(region, date) %>% 
                summarise(daily.so = mean(so.total), 
                          daily.pi = mean(pi.total),
                          daily.cu = mean(cu.total),
                          daily.co = mean(co.total),
                          daily.he = mean(he.total),
                          daily.ck = mean(ck.total)) %>% 
                ungroup()

js_cum_abund <- cum_abund %>% 
                filter(region == "JS") %>% 
                transmute(date = date, region = region,
                              so.cum.abund = cumsum(daily.so), 
                              pi.cum.abund = cumsum(daily.pi),
                              cu.cum.abund = cumsum(daily.cu),
                              co.cum.abund = cumsum(daily.co),
                              he.cum.abund = cumsum(daily.he),
                              ck.cum.abund = cumsum(daily.ck)
                              ) %>% 
                 gather(so.cum.abund, pi.cum.abund, cu.cum.abund,
                           co.cum.abund, he.cum.abund, ck.cum.abund, key = "species", value = "cum.abund") %>% 
                ungroup()

di_cum_abund <- cum_abund %>% 
                filter(region == "DI") %>% 
                transmute(date = date, region = region,
                              so.cum.abund = cumsum(daily.so), 
                              pi.cum.abund = cumsum(daily.pi),
                              cu.cum.abund = cumsum(daily.cu),
                              co.cum.abund = cumsum(daily.co),
                              he.cum.abund = cumsum(daily.he),
                              ck.cum.abund = cumsum(daily.ck)
                              ) %>% 
                 gather(so.cum.abund, pi.cum.abund, cu.cum.abund,
                           co.cum.abund, he.cum.abund, ck.cum.abund, key = "species", value = "cum.abund")  

cum_abund <- rbind(di_cum_abund,js_cum_abund)

labels <- c(DI = "Discovery Islands", JS = "Johnstone Strait")

cum_abund_plot <- ggplot(data = cum_abund, mapping = aes(x = date, y = cum.abund)) +
        geom_point(mapping = aes(colour= species)) +
        geom_line(mapping = aes(colour = species)) +
        ylab("Cumulative abundance") + xlab("Date") + 
        facet_grid(region ~., labeller=labeller(region = labels))+
        scale_colour_discrete(name = "",
                        breaks=c("co.cum.abund","cu.cum.abund", "he.cum.abund", "pi.cum.abund", "so.cum.abund",
                                 "ck.cum.abund"),
                        labels=c("Coho", "Chum", "Herring", "Pink", "Sockeye", "Chinook"))+
        theme(legend.justification=c(1,0),
                legend.background = element_rect(fill="white")) +  
        theme(legend.text = element_text(colour="black", size = 12))+ 
        theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))+
        theme(legend.justification=c(1,0), legend.position=c(.3,.6),
             legend.background = element_rect(fill="white")) 
cum_abund_plot 
ggsave("./final_figures/all_spp_cumulative_abundance.png")

```

### Cumulative Abundance of Sockeye by Region
```{r Sockeye Cumulative Abundance, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The cumulative abundance of sockeye captured in the Discovery Islands and Johnstone Strait in 2017."}
# Create new columns for cumulative sums of each species captured
# Average multiple seines conducted in the same region on the same day

# This summarises and averages cpue grouped by region and sampling day
cum_abund_by_region <- field_2017 %>% 
                filter(!survey.id %in% c("DE457","DE458","DE459","DE460","DE461","DE462","DE463","DE464")) %>%
                        # The line above removes Sam James's MSc seines from this analysis becuse they are outside the 
                        # standardized effort required for cumulative abundance analysis to be unbiased. 
                select(date, region, so.total,pi.total,cu.total,co.total, he.total) %>%
                replace(is.na(.),0) %>% 
                na.omit() %>% 
                group_by(region, date) %>% 
                summarise(daily.so = mean(so.total), 
                          daily.pi = mean(pi.total),
                          daily.cu = mean(cu.total),
                          daily.co = mean(co.total),
                          daily.he = mean(he.total)
                )

# This replaces cpue for each day and each region with the cumulative sum for each species, and then tidys the data so that each row is only one observation
cum_abund_by_region <- cum_abund_by_region %>% 
                    transmute(date = date,
                              so.cum.abund = cumsum(daily.so), 
                              pi.cum.abund = cumsum(daily.pi),
                              cu.cum.abund = cumsum(daily.cu),
                              co.cum.abund = cumsum(daily.co),
                              he.cum.abund = cumsum(daily.he)
                              ) %>% 
                    gather(so.cum.abund, pi.cum.abund, cu.cum.abund,
                           co.cum.abund, he.cum.abund, key = "species", value = "cum.abund")        

# This plots cumulative abundnace of sockeye grouped by region

so_cum_abund_plot <- ggplot(data = filter(cum_abund_by_region, species == "so.cum.abund"),
        mapping = aes(x = date, y = cum.abund)) +
        geom_point(mapping = aes(colour= region)) +
        geom_line(mapping = aes(colour = region)) +
        ylab("Sockeye cumulatve abundance") + xlab("Date") +
        scale_colour_discrete(name = "",
                        breaks=c("DI","JS"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
        theme(legend.justification=c(1,0),legend.background = element_rect(fill="white")) +  
                theme(legend.text = element_text(colour="black", size = 12)) +                         theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))+
        theme(legend.justification=c(1,0), legend.position=c(.4,.8),
             legend.background = element_rect(fill="white")) 
so_cum_abund_plot
ggsave("./final_figures/sockeye_cumulative_abundance.png")



```

### Sockeye Catch Per Unit Effort

```{r Sockeye CPUE, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="Catch per unit effort of juvenile sockeye salmon in 2017 averaged over one week periods for each region."}

so_cpue <- field_2017 %>%
        replace(is.na(.),0) %>%
        group_by(region, date, sampling.week) %>% 
        summarise(so.cpue = mean(so.total, na.rm = TRUE), 
                  so.cpue.sd = sd(so.total, na.rm = T),
                  n = n()) %>% 
        mutate(SE = so.cpue.sd / sqrt(n)) %>% 
        ungroup() %>% 
        group_by(region, sampling.week) %>% 
        summarise(so.cpue = mean(so.cpue, na.rm = TRUE), 
                  so.cpue.sd = sd(so.cpue, na.rm = T),
                  n = n()) # Eventually I should correct these SE bars because they show SE of the sampling weeks means of the daily means



so_cpue$sampling.week <- as.factor(so_cpue$sampling.week)

so_cpue_plot <- ggplot(data = so_cpue, aes(x = sampling.week, y = so.cpue, colour = region, group = region))+
        geom_line()+
        geom_point(position = position_dodge(width = 0.05))+
        #geom_errorbar(aes(ymin = so.cpue - SE, ymax = so.cpue + SE), width = 0.2, position = position_dodge(width = 0.15))+
        xlab("Date") +
        ylab("Sockeye CPUE") +
        coord_cartesian(ylim= 0:300, xlim = 1:11) +
        scale_x_discrete(breaks=c("2","3","4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 12","May 19","May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
        scale_colour_discrete(name = "",
                        breaks=c("DI","JS"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
        theme(legend.justification=c(1,0), legend.position=c(.4,.8),
             legend.background = element_rect(fill="white")) + 
                theme(legend.text = element_text(colour="black", size = 12)) +                         theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))
so_cpue_plot        
ggsave("./final_figures/Sockeye_CPUE.png")


```

\newpage

## Parasite Loads 

### Definitions[^1] 

_Prevalence_: Number of individuals of a host species infected with a particular parasite species ÷ Number of hosts examined. 

_Mean Infection Intensity_: Total number of individuals
of a particular parasite species
in a sample of a host species ÷ Number
of infected individuals of the host
species in the sample (= Mean number
of individuals of a particular parasite
species per infected host in a sample). 

_Abundance_: The total number of individuals of a particular parasite species in a sample of hosts ÷ Total number of individuals of the host species in the sample.

[^1]: Margolis, L., Esch, G.W., Holmes, J.C., Kuris, A.M. and Schad, G.A. (1982). The use of ecological terms in parasitology: report of an ad hoc committee of the American Society of Parasitologists. J. Parasitol. 68:131–133.

### Sea Lice Prevalence


```{r Lice Prevalence, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "The proportion of juvenile sockeye that had at least one sea louse of any developmental stage of both _Lepeoptheirus salmonis_ and _Caligus clemensi_ in the Discovery Islands and Johnstone Strait in 2017."}

# Group fish by region and by sampling week to calculate prevalence of sea-lice
sea_lice_2017_summary <- sea_lice_2017 %>%
        mutate(total.lice = cal.cope + lep.cope + chal.a +
                        chal.b + cal.mot + gc + palm + palf + lam + laf + gl
                        + unid.cope + unid.chal,
               copepodid = cal.cope + lep.cope + unid.cope,
               chalimus = chal.a + chal.b + unid.chal,
               motile = cal.mot + gc + palm + palf + lam + laf + gl,
               motile.caligus = cal.mot + gc,
               motile.lep = palm + palf + lam + laf + gl
        )

# Summarize data to calcuate the average prevalence by region and sampling week with SD
sea_lice_2017_prevalence <- sea_lice_2017_summary %>%
                group_by(region, sampling.week) %>%
                summarize(prevalence = mean(total.lice > 0))
                

#Need to make the sampling week a categorical variable
sea_lice_2017_prevalence$sampling.week <- as.factor(sea_lice_2017_prevalence$sampling.week)

sea_lice_2017_prevalence_plot <- ggplot(data = sea_lice_2017_prevalence, aes(x = sampling.week, y = prevalence, colour = region, group = region))+
                geom_point(position = position_dodge(0.05))+
                geom_line()+
                ylab("Prevalence")+
                xlab("Date")+
                scale_x_discrete(breaks=c("4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
                scale_color_discrete(name = "",
                        breaks=c("DI", "JS"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
                theme(legend.justification=c(1,0),legend.background = element_rect(fill="white"))+
                theme(legend.text = element_text(colour="black", size = 12)) + 
                theme(axis.text=element_text(size=12),
                        axis.title=element_text(size=12,face="bold"))+
                coord_cartesian(y= 0:1)+
                theme(legend.justification=c(1,0), legend.position=c(.4,.2),
                        legend.background = element_rect(fill="white")) 

sea_lice_2017_prevalence_plot
ggsave("./final_figures/sea_lice_prevalence.png")

               
```

 
\newpage

### Sea Lice Infection Abundance

```{r Lice Abundance, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "The abundance ± SE of three developmental stages of both _Lepeoptheirus salmonis_ and _Caligus clemensi_ sea lice per juvenile sockeye salmon."}


sea_lice_2017_avg <- sea_lice_2017_summary %>%
                select(region, sampling.week, copepodid, chalimus, motile) %>% 
                group_by(region, sampling.week) %>%
                summarise(
                        cope    = mean(copepodid, na.rm = T),
                        chal    = mean(chalimus, na.rm = T),
                        mot     = mean(motile, na.rm =T)) %>%
                gather(cope, chal, mot, key = "life.stage", value = "abundance") 

sea_lice_2017_se <- sea_lice_2017_summary %>% 
                select(region, sampling.week, copepodid, chalimus, motile) %>% 
                        group_by(region, sampling.week) %>%
                        summarise(
                                cope = sd(copepodid, na.rm = T)/sqrt(n()),  
                                chal = sd(chalimus, na.rm = T)/sqrt(n()),  
                                mot  = sd(motile, na.rm = T )/sqrt(n())) %>% 
                        gather(cope, chal, mot, key = life.stage, value = "se")

sea_lice_2017_avg$se <- sea_lice_2017_se$se

sea_lice_2017_avg$sampling.week <- as.factor(sea_lice_2017_avg$sampling.week)
stages <- c("cope", "chal", "mot")
sea_lice_2017_avg$life.stage <- factor(sea_lice_2017_avg$life.stage, levels = c("cope", "chal", "mot"))

#Plot abundnace

labels <- c('DI' = "Discovery Islands", 'JS' = "Johnstone Strait")


sea_lice_2017_abundance_plot <- ggplot(data = sea_lice_2017_avg, aes(x = sampling.week, y = abundance, fill = life.stage))+
                geom_bar(position = position_dodge(), stat= "identity")+
                geom_errorbar(aes(ymin = abundance-se, ymax = abundance+se), 
                              width = .2,
                              position = position_dodge(.9))+
                facet_grid(region ~., labeller = as_labeller(labels))+ 
                ylab("Abundance")+
                xlab("Date")+
                scale_x_discrete(breaks=c("4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
                scale_fill_discrete(name = "",
                        breaks=c("cope", "chal", "mot"),
                        labels=c("Copepodid", "Chalimus", "Motile"))+
                theme(legend.justification=c(1,0), legend.position=c(.3,.14),
                      legend.background = element_rect(fill="white")) +  
                theme(legend.text = element_text(colour="black", size = 12)) +                            theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))
sea_lice_2017_abundance_plot
ggsave("final_figures/sea_lice_abundance.png")

```



### Motile Infection Abundance by Species

```{r Motile Caligus and Lep abundance, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The abundance  ± SE of __motile__ _Lepeoptheirus salmonis_ and _Caligus clemensi_ sea lice combined infecting juvenile sockeye salmon in the Discovery Islands and Johnstone Strait in 2017."}

sea_lice_2017_mot <- sea_lice_2017_summary %>% 
                select(region, sampling.week, motile.caligus, motile.lep) %>% 
                group_by(region, sampling.week) %>%
                summarise(
                        cal    = mean(motile.caligus, na.rm = T),
                        lep    = mean(motile.lep, na.rm = T)) %>%
                gather(cal, lep, key = "species", value = "abundance") 

sea_lice_2017_mot_se <- sea_lice_2017_summary %>% 
                select(region, sampling.week, motile.caligus, motile.lep) %>% 
                        group_by(region, sampling.week) %>%
                        summarise(
                                cal = sd(motile.caligus, na.rm = T)/sqrt(n()),  
                                lep = sd(motile.lep, na.rm = T)/sqrt(n())) %>% 
                        gather(cal, lep, key = species, value = "se")

sea_lice_2017_mot$se <- sea_lice_2017_mot_se$se

sea_lice_2017_mot$sampling.week <- as.factor(sea_lice_2017_mot$sampling.week)

motile_abundance_plot <- ggplot(sea_lice_2017_mot, aes(x = sampling.week, y = abundance, colour = species, group = species))+
        geom_point()+
        geom_line()+
        geom_errorbar(aes(ymin = abundance - se, ymax = abundance + se, width = 0.1))+
        facet_grid(region~., labeller = as_labeller(labels))+
        xlab("Date")+
        ylab("Infection Abundance")+
                scale_x_discrete(breaks=c("4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
                scale_colour_discrete(name = "",
                        breaks=c("cal", "lep"),
                        labels=c("Caligus clemensi", "Lepeioptheirus salmonis"))+
                theme(legend.justification=c(1,0), legend.position=c(.4,.3),
                      legend.background = element_rect(fill="white")) +  
                theme(legend.text = element_text(colour="black", size = 12, face = "italic")) +                            theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))
        
motile_abundance_plot
ggsave("final_figures/mot_abundance.png")

```

\newpage


### Sea Lice Infection Intensity

```{r infection intensity all life stages, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The mean infection intensity of all life stages of both _Lepeoptheirus salmonis_ and  _Caligus clemensi_ sea lice on juvenile sockeye salmon in the Discovery Islands and Johnstone Strait in 2017."}

sea_lice_2017_intensity <- sea_lice_2017_summary %>% 
                filter(total.lice > 0) %>% 
                select(region, sampling.week, total.lice) %>% 
                group_by(region, sampling.week) %>%
                summarise(
                        intensity =  mean(total.lice, na.rm = T))

sea_lice_2017_intensity_se <- sea_lice_2017_summary %>%
                filter(total.lice > 0) %>% 
                select(region, sampling.week, total.lice) %>% 
                        group_by(region, sampling.week) %>%
                        summarise(
                                se = sd(total.lice, na.rm = T)/sqrt(n()))

sea_lice_2017_intensity$se <- sea_lice_2017_intensity_se$se

sea_lice_2017_intensity$sampling.week <- as.factor(sea_lice_2017_intensity$sampling.week)

sea_lice_intensity_plot <- ggplot(sea_lice_2017_intensity, aes(x = sampling.week, y = intensity, group = region))+
        geom_point()+
        geom_line()+
        geom_errorbar(aes(ymin = intensity - se, ymax = intensity + se, width = 0.1))+
        facet_grid(region~., labeller = as_labeller(labels))+
        xlab("Date")+
        ylab("Mean Infection Intensity")+
                scale_x_discrete(breaks=c("4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
                theme(legend.justification=c(1,0), legend.position=c(.4,.3),
                      legend.background = element_rect(fill="white")) +  
                theme(legend.text = element_text(colour="black", size = 12, face = "italic")) +                            theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))
        
sea_lice_intensity_plot
ggsave("final_figures/cal_mot_intensity_plot.png") 

```

\newpage

#### Motile _Caligus clemensi_ Infection Intensity 
```{r Lice cal intensity, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The mean infection intensity of __motile__ _Caligus clemensi_ sea lice per juvenile sockeye salmon infected with one or more motile _Caligus clemensi_."}

sea_lice_2017_cal_mot_intensity <- sea_lice_2017_summary %>% 
                filter(motile.caligus > 0) %>% 
                select(region, sampling.week, motile.caligus) %>% 
                group_by(region, sampling.week) %>%
                summarise(
                        intensity =  mean(motile.caligus, na.rm = T))

sea_lice_2017_cal_mot_intens_se <- sea_lice_2017_summary %>%
                filter(motile.caligus > 0) %>% 
                select(region, sampling.week, motile.caligus) %>% 
                        group_by(region, sampling.week) %>%
                        summarise(
                                se = sd(motile.caligus, na.rm = T)/sqrt(n()))

sea_lice_2017_cal_mot_intensity$se <- sea_lice_2017_cal_mot_intens_se$se

sea_lice_2017_cal_mot_intensity$sampling.week <- as.factor(sea_lice_2017_cal_mot_intensity$sampling.week)

cal_mot_intensity_plot <- ggplot(sea_lice_2017_cal_mot_intensity, aes(x = sampling.week, y = intensity, group = region))+
        geom_point()+
        geom_line()+
        geom_errorbar(aes(ymin = intensity - se, ymax = intensity + se, width = 0.1))+
        facet_grid(region~., labeller = as_labeller(labels))+
        xlab("Date")+
        ylab("Mean Infection Intensity")+
                scale_x_discrete(breaks=c("4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
                theme(legend.justification=c(1,0), legend.position=c(.4,.3),
                      legend.background = element_rect(fill="white")) +  
                theme(legend.text = element_text(colour="black", size = 12, face = "italic")) +                            theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))
        
cal_mot_intensity_plot
ggsave("final_figures/cal_mot_intensity_plot.png") 

```

\newpage

#### Motile _Lepeoptheirus salmonis_ Infection Intensity

```{r Lice lep intensity, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The mean intensity of __motile__ _Lepeoptheirus salmonis_ sea lice per juvenile sockeye salmon infected with one or more motile _Lepeoptheirus salmonis_."}

sea_lice_2017_lep_mot_intensity <- sea_lice_2017_summary %>% 
                filter(motile.lep > 0) %>% 
                select(region, sampling.week, motile.lep) %>% 
                group_by(region, sampling.week) %>%
                summarise(
                        intensity =  mean(motile.lep, na.rm = T))

sea_lice_2017_lep_mot_intens_se <- sea_lice_2017_summary %>%
                filter(motile.lep > 0) %>% 
                select(region, sampling.week, motile.lep) %>% 
                        group_by(region, sampling.week) %>%
                        summarise(
                                se = sd(motile.lep, na.rm = T)/sqrt(n()))

sea_lice_2017_lep_mot_intensity$se <- sea_lice_2017_lep_mot_intens_se$se

sea_lice_2017_lep_mot_intensity$sampling.week <- as.factor(sea_lice_2017_lep_mot_intensity$sampling.week)

lep_mot_intensity_plot <- ggplot(sea_lice_2017_lep_mot_intensity, aes(x = sampling.week, y = intensity, group = region))+
        geom_point()+
        geom_line()+
        geom_errorbar(aes(ymin = intensity - se, ymax = intensity + se, width = 0.1))+
        facet_grid(region~., labeller = as_labeller(labels))+
        xlab("Date")+
        ylab("Mean Infection Intensity")+
                scale_x_discrete(breaks=c("4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
                theme(legend.justification=c(1,0), legend.position=c(.4,.3),
                      legend.background = element_rect(fill="white")) +  
                theme(legend.text = element_text(colour="black", size = 12, face = "italic")) +                            theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))
        
lep_mot_intensity_plot
ggsave("final_figures/lep_mot_intensity_plot.png")

```


\newpage



## Fish Length and Weight
### Sockeye Length
```{r Length Histogram, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "Length frequency histogram of juvenile sockeye in the Discovery Islands and Johnstone Strait in 2017."}
length_histo <- ggplot(sea_lice_2017, aes(x=fork.length))+
  geom_histogram(aes(y=5*..density..*100),
                 alpha=1, position='identity', binwidth=9)+
  xlab("Fork Length (mm)")+
  ylab("Frequency (%)")+
  coord_cartesian(x= 60:170) +
        theme(legend.text = element_text(colour="black", size = 12)) +                            theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))
length_histo
ggsave("./final_figures/sockeye_length_histo_2017.png", width = 9, height = 9)
```

### Sockeye Weight
```{r Weight Histogram, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "Weight frequency histogram of juvenile sockeye salmon in the Discovery Islands and Johnstone Strait in 2017."}
weight_histo <- ggplot(sea_lice_2017, aes(x=weight))+
  geom_histogram(aes(y=5*..density..*100),
                 alpha=1, position='identity', binwidth=4)+
  xlab("Weight (g)")+
  ylab("Frequency (%)")+
  coord_cartesian(x= 0:50)+
        theme(legend.text = element_text(colour="black", size = 12)) +                            theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))

weight_histo
ggsave("./final_figures/sockeye_length_histo_2017.png")
```



```{r Sea Surface Temp, include = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "Sea surface temperature in the Discovery Islands and Johnstone Strait averaged by date and region in 2017."}

ysi_data <- ysi_data %>% 
                group_by(Survey, Date) %>% 
                summarise(avg.temp = mean(temp))

sst_plot <- ggplot(ysi_data, aes(x = Date, y = avg.temp, colour = Survey, group = Survey)) +
        geom_point() +
        geom_line() +
        theme(legend.text = element_text(colour="black", size = 12),
              axis.text=element_text(size=12),axis.title=element_text(size=12,face="bold")) +
         scale_color_discrete(name = "",
                        breaks=c("DISOCKEYE", "JSSOCKEYE"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
        ylab("Average temperature (ºC)")+
        theme(legend.justification=c(1,0), legend.position=c(.4,.8),
             legend.background = element_rect(fill="white")) 

sst_plot
ggsave("./final_figures/sst_plot.png")


```

## Oceanographic Conditions
### Chlorophyll a

```{r Chl_a, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap=" Surface chlorophyll a concentrations in the Disocovery Islands and the northern Strait of Georgia in 2017. See Figure 1 for station locations."}

sites <- c("QU39", "QU29")
chl_a_data <- chl_a_data %>% 
        filter(Filter.Type == "Bulk GF/F", Line.Out.Depth <= 30,
               Date > "2017-03-15", Site.ID %in% sites) %>% 
        group_by(Date, Site.ID) %>% 
        summarise(chl_a_avg = mean(Chla)) %>% 
        na.omit()
 
chl_a_plot <- ggplot(data = chl_a_data, aes(x = Date, y = chl_a_avg, color = Site.ID)) +
        geom_point() + 
        geom_line() +
        ylab("Chlorophyll a (mg/m^3)") +
        scale_color_discrete(name = "",
                        breaks=c("QU29", "QU39"),
                        labels=c("Discovery Islands (QU29)", "Northern Strait of Georgia (QU39)"))+
        theme(legend.text = element_text(colour="black", size = 12),
              axis.text=element_text(size=12),axis.title=element_text(size=12,face="bold")) +
        theme(legend.justification=c(1,0), legend.position=c(.9,.8),
              legend.background = element_rect(fill="white"))   
        
        
chl_a_plot
ggsave("./final_figures/chl_a_plot.png")

```

### Temperature 

```{r CTD 30 m integrated temp, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "Average temperature of the top 30 m of the water column in the Disocvery Islands and Johnstone Strait in 2017."}




ctd_data_temp_js <- js_ctd %>% 
        filter(Depth <= 30) %>% 
        group_by(region, date) %>% 
        summarise(avg.temp = mean(Temperature, na.rm = T))

ctd_data_temp_di <- di_ctd %>% 
        filter(Depth <= 30) %>% 
        group_by(region, date) %>% 
        summarise(avg.temp = mean(Temperature, na.rm = T))


ctd_data_temp <- rbind(ctd_data_temp_di,ctd_data_temp_js)

ctd_data_temp$region <- as_factor(ctd_data_temp$region)
ctd_data_temp$date <- ymd(ctd_data_temp$date)

int._30m_temp_plot <- ggplot(ctd_data_temp, aes(x = date, y= avg.temp, colour = region))+
        geom_line() +
        geom_point()+
        ylab("Temperature (ºC)")+
        xlab("Date")+
        scale_color_discrete(name = "",
                        breaks=c("DI", "JS"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
        theme(legend.text = element_text(colour="black", size = 12),
              axis.text=element_text(size=12),axis.title=element_text(size=12,face="bold")) +
        theme(legend.justification=c(1,0), legend.position=c(.35,.8),
              legend.background = element_rect(fill="white")) +
        scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%B %d") + 
        theme(axis.text.x  = element_text(angle=35, vjust = 0.3))
        

int._30m_temp_plot
ggsave("./final_figures/integrated_temp.png")
```


```{r Flurometry, include = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "Fluorometry " }

ctd_data <- rbind(js_ctd, di_ctd)

ctd_data_flurometry <- ctd_data %>% 
        filter(Depth <= 30) %>%
        group_by(region,date) %>% 
        summarize(Fluorometry.Chlorophyll = mean(Fluorometry.Chlorophyll))

fluoromtery_plot <- ggplot(ctd_data_flurometry, aes(x = date, y = Fluorometry.Chlorophyll, colour = region))+
        geom_point()+
        geom_line()
fluoromtery_plot
```

## Highlights
* Sampling has finished for the 2017 smolt migration
* Sockeye arrived later in 2017 than in 2015 and 2016
* Sockeye finished passing through the study region at a similar date as in 2015 and 2016
* Chum abundance is high in 2017
* Very few _Lep._ sea lice