---
title: "Juvenile Salmon Report"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    navbar:
      - { title: "About", href: "https://example.com/about", align: left }
    social: menu
    theme : readable
    logo: Hakai_red.png
    favicon: Hakai_red.png
runtime: shiny
---

```{r global, include = FALSE}
library(shiny)
library(flexdashboard)
library(tidyverse)
source(file = "./raw_scripts/pre-process.R")


theme_set(theme_classic(base_size = 14))
```

Analysis {.storyboard}
=========================================

### Cumulative Abundance of Sockeye by Region
```{r}
# Create new columns for cumulative sums of each species captured
# Average multiple seines conducted in the same region on the same day

# This summarises and averages cpue grouped by region and sampling day
cum_abund_by_region <- field_2017 %>% 
                select(date, region, so.total,pi.total,cu.total,co.total, he.total) %>%
                na.omit() %>% 
                group_by(region, date) %>% 
                summarise(daily.so = mean(so.total), 
                          daily.pi = mean(pi.total),
                          daily.cu = mean(cu.total),
                          daily.co = mean(co.total),
                          daily.he = mean(he.total)
                )

# This replaces cpue for each day and each region with the cumulative sum for each species, and then tidys the data so that each row is only one observation
cum_abund_by_region <- cum_abund_by_region %>% 
                    transmute(date = date,
                              so.cum.abund = cumsum(daily.so), 
                              pi.cum.abund = cumsum(daily.pi),
                              cu.cum.abund = cumsum(daily.cu),
                              co.cum.abund = cumsum(daily.co),
                              he.cum.abund = cumsum(daily.he)
                              ) %>% 
                    gather(so.cum.abund, pi.cum.abund, cu.cum.abund,
                           co.cum.abund, he.cum.abund, key = "species", value = "cum.abund")        

# This plots cumulative abundnace of sockeye grouped by region

so_cum_abund_plot <- ggplot(data = filter(cum_abund_by_region, species == "so.cum.abund"),
        mapping = aes(x = date, y = cum.abund)) +
        geom_point(mapping = aes(colour= region)) +
        geom_line(mapping = aes(colour = region)) +
        ylab("Sockeye Cumulatve Abundance") + xlab("Date") +
        scale_colour_discrete(name = "",
                        breaks=c("DI","JS"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
        theme(legend.justification=c(1,0), legend.position=c(.4,.7),
                axis.title.x=element_blank(),legend.background = element_rect(fill="white")) +  
                theme(legend.text = element_text(colour="black", size = 14)) + theme(axis.text=element_text(size=14),
                axis.title=element_text(size=14,face="bold"))
ggsave("./final_figures/sockeye_cumulative_abundance.pdf")

so_cum_abund_plot
```

***
The cumulative abundance of sockeye salmon smolts captured by the Hakai Institute's 
Juvenile Salmon Program grouped by the two samping nodes of the project in the Discovery
Islands and Johnstone Strait.


### Cumulative Abundance of Sockeye, Pink, Chum, Coho, Herring 

```{r}
# This calculates cumulative abundance, regardless of region
cum_abund <- field_2017 %>% 
                select(date, so.total, pi.total, cu.total, co.total, he.total) %>%
                na.omit() %>% 
                group_by(date) %>% 
                summarise(daily.so = mean(so.total), 
                          daily.pi = mean(pi.total),
                          daily.cu = mean(cu.total),
                          daily.co = mean(co.total),
                          daily.he = mean(he.total)
                )

cum_abund <- cum_abund %>% 
                    transmute(date = date,
                              so.cum.abund = cumsum(daily.so), 
                              pi.cum.abund = cumsum(daily.pi),
                              cu.cum.abund = cumsum(daily.cu),
                              co.cum.abund = cumsum(daily.co),
                              he.cum.abund = cumsum(daily.he)
                              ) %>% 
                    gather(so.cum.abund, pi.cum.abund, cu.cum.abund,
                           co.cum.abund, he.cum.abund, key = "species", value = "cum.abund")  

cum_abund_plot <- ggplot(data = cum_abund, mapping = aes(x = date, y = cum.abund)) +
        geom_point(mapping = aes(colour= species)) +
        geom_smooth(mapping = aes(colour = species)) +
        ylab("Cumulative Abundance") + xlab("Date") + 
        scale_colour_discrete(name = "Species",
                        breaks=c("co.cum.abund","cu.cum.abund", "he.cum.abund", "pi.cum.abund", "so.cum.abund"),
                        labels=c("Coho", "Chum", "Herring", "Pink", "Sockeye"))+
        theme_classic(base_size = 20)+
        theme(legend.justification=c(1,0),
                legend.position=c(.35,.6), axis.title.x=element_blank(),
                legend.background = element_rect(fill="white")) +  
        theme(legend.text = element_text(colour="black", size = 14))+ 
        theme(axis.text=element_text(size=14),
                axis.title=element_text(size=14,face="bold"))
cum_abund_plot
ggsave("./final_figures/all_spp_cumulative_abundance.pdf")

```

***
The cumulative abundance of fish caught in both the Discovery Islands and
Johnstone Strait.


### Sockeye CPUE
```{r}
so_cpue <- field_2017 %>% 
        group_by(region, sampling.week) %>% 
        summarise(so.cpue = mean(so.total, na.rm = TRUE), 
                  so.cpue.sd = sd(so.total, na.rm = T),
                  n = n()) %>% 
        mutate(SE = so.cpue.sd / sqrt(n))

so_cpue$sampling.week <- as.factor(so_cpue$sampling.week)

so_cpue_plot <- ggplot(data = so_cpue, aes(x = sampling.week, y = so.cpue, colour = region))+
        geom_point()+
        geom_errorbar(aes(ymin = so.cpue - SE, ymax = so.cpue + SE), width = 0.2)+
        geom_smooth(se = F) +
        xlab("Date") +
        ylab("Sockeye CPUE") +
        coord_cartesian(ylim= 0:1000, xlim = 3:11) +
        scale_x_discrete(breaks=c("4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
        scale_colour_discrete(name = "",
                        breaks=c("DI","JS"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
        theme(legend.justification=c(1,0), legend.position=c(.5,.8),
                axis.title.x=element_blank(),legend.background = element_rect(fill="white"))
so_cpue_plot        
        ggsave("./final_figures/Sockeye_CPUE.pdf")


```

***
The catch per unit effort (CPUE) of juvenile sockeye salmon in the Discovery Islands and Johnstone Strait averaged over 1 week periods with standard error bars.


### Sea Lice Abundance
```{r}
### This whole section is un-tested because I didn't create test data

# Group fish by region and by sampling week to calculate prevalence of sea-lice
sea_lice_2017_summary <- sea_lice_2017 %>%
        mutate(total.lice = cal.cope + lep.cope + chal.a +
                        chal.b + cal.mot + gc + palm + palf + lam + laf + gl
                        + unid.cope + unid.chal,
               copepodid = cal.cope + lep.cope + unid.cope,
               chalimus = chal.a + chal.b + unid.chal,
               motile = cal.mot + gc + palm + palf + lam + laf + gl
        )

sea_lice_2017_avg <- sea_lice_2017_summary %>%
                select(region, sampling.week, copepodid, chalimus, motile) %>% 
                group_by(region, sampling.week) %>%
                summarise(
                        cope    = mean(copepodid, na.rm = T),
                        chal    = mean(chalimus, na.rm = T),
                        mot     = mean(motile, na.rm =T)) %>%
                # Need to fix this gather, I don't think it's right
                gather(cope, chal, mot, key = "life.stage", value = "abundance") 

sea_lice_2017_se <- sea_lice_2017_summary %>% 
                select(region, sampling.week, copepodid, chalimus, motile) %>% 
                        group_by(region, sampling.week) %>%
                        summarise(
                                cope = sd(copepodid, na.rm = T)/sqrt(n()),  
                                chal = sd(chalimus, na.rm = T)/sqrt(n()),  
                                mot  = sd(motile, na.rm = T )/sqrt(n())) %>% 
                        gather(cope, chal, mot, key = life.stage, value = "sd")

sea_lice_2017_avg <- inner_join(sea_lice_2017_avg, sea_lice_2017_se, by = "life.stage")
rm(sea_lice_2017_se)
sea_lice_2017_avg$sampling.week.x <- as.factor(sea_lice_2017_avg$sampling.week.x)
stages <- c("cope", "chal", "mot")
sea_lice_2017_avg$life.stage <- factor(sea_lice_2017_avg$life.stage, levels = c("cope", "chal", "mot"))

#Plot abundnace
sea_lice_2017_abundance_plot <- ggplot(data = sea_lice_2017_avg, aes(x = sampling.week.x, y = abundance, fill = life.stage))+
                geom_bar(stat= "identity", position = position_dodge())+
                geom_errorbar(aes(ymin = abundance - sd, ymax = abundance + sd), width = 0.2,
                              position = position_dodge(0.9))+
                facet_wrap(~region.x, nrow = 2) +
                ylab("Lice per fish")+
                xlab("Date")+
                scale_x_discrete(breaks=c("4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
                scale_fill_discrete(name = "Louse Developmental Stage",
                        breaks=c("cope", "chal", "mot"),
                        labels=c("Copepodid", "Chalimus", "Motile"))+
                theme(legend.justification=c(1,0), legend.position=c(.45,.805),
                        axis.title.x=element_blank(),legend.background = element_rect(fill="white"))
sea_lice_2017_abundance_plot
ggsave("final_figures/sea_lice_abundance.pdf")


```

### Sea Lice Prevalence

```{r}
# Summarize data to calcuate the average prevalence by region and sampling week with SD
sea_lice_2017_prevalence <- sea_lice_2017_summary %>%
                group_by(region, sampling.week) %>%
                summarize(lice.present = mean(total.lice > 0)) %>%
                mutate(se = sd(lice.present) / sqrt(n()))

#Need to make the sampling week a categorical variable
sea_lice_2017_prevalence$sampling.week <- as.factor(sea_lice_2017_prevalence$sampling.week)

sea_lice_2017_prevalence_plot <- ggplot(data = sea_lice_2017_prevalence, aes(x = sampling.week, y = lice.present, colour = region))+
                geom_point()+
                geom_line()+
                ylab("Lice per sockeye")+
                xlab("Date")+
                scale_x_discrete(breaks=c("4", "5", "6", "7", "8", "9", "10", "11"),
                        labels=c("May 26", "June 2", "June 9", "June 16",
                         "June 23", "June 30", "July 6", "July 14")) +
                scale_color_discrete(name = "Region",
                        breaks=c("DI", "JS"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
                theme(legend.justification=c(1,0), legend.position=c(.45,.805),
                        axis.title.x=element_blank(),legend.background = element_rect(fill="white"))

sea_lice_2017_prevalence_plot

# 
#                 
```


### Fish Length
```{r}

```

***
Commentary for frame 4


### Fish Weight

```{r}
```
***
Commentary for frame 5


### Oceanographic Conditions
```{r}
```
***
Commentary for frame 6