---
title: "Hakai Institute Juvenile Salmon Program Report"
output:
  rmarkdown::pdf_document:
    
    fig_caption: yes
    includes:
      in_header: figure_opts.tex
    latex_engine: xelatex
sansfont: Times New Roman
fontsize: 12pt

header-includes:
- \usepackage{booktabs}
- \usepackage{sectsty} \sectionfont{\centering \emph}
      
---

\begin{center}
\large
— Hakai Institute Juvenile Salmon Program —
\end{center}

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE)
library(tidyverse)
library(lubridate)
library(here)
library(googlesheets)
library(ggridges)
options(scipen=999) # This removes scientific notation for inline output ie `r object` in the report text
```

```{r setup}
field_2018 <- gs_key("1iRQCKMTznHbMeI9GunbsgPyb-rtWgwj-0IfxLw7NBJE", 
                         lookup = FALSE, visibility = "private")

survey_data <- gs_read(field_2018, ws = "survey_data")

survey_data <- survey_data %>% 
  mutate(sampling_week = as.numeric((yday(survey_date) + 4) %/% 7))

survey_data$sampling_week <- recode_factor(survey_data$sampling_week, 
                                       `18` = "May 5",
                                       `19` = "May 12" ,
                                       `20` = "May 19", 
                                       `21` = "May 26",
                                       `22` = "June 2",
                                       `23` = "June 9", 
                                       `24` = "June 16", 
                                       `25` = "June 23",
                                       `26` = "June 30", 
                                       `27` = "July 6", 
                                       `28` = "July 13")

seine_data <- gs_read(field_2018, ws = "seine_data")

survey_seines <- left_join(seine_data, survey_data) %>% 
    mutate(year = year(survey_date))

fish_and_sealice_field_data <- gs_read(field_2018, 
                                       ws = "fish_and_sealice_field_data")

fish_and_sealice_field_data <- left_join(fish_and_sealice_field_data, 
                                         survey_seines, by = "seine_id")
```


## Aim 

To provide regular in-season summaries of juvenile Fraser salmon migration catch statistics, health indices, and oceanographic conditions in the northern Strait of Georgia to Johnstone Strait region. 

## Background

The Hakai Institute Juvenile Salmon Program was launched in the spring of 2015 in a collaborative partnership with UBC, SFU, Salmon Coast, Pacific Salmon Foundation, and DFO. The program operates in the Discovery Islands and Johnstone Strait (Figure 1) and thus provides information on the health of juvenile Fraser River salmon after passage through: 

1) Strait of Georgia – stratified high plankton biomass zone; and 

2) Discovery Islands & Johnstone Strait – highly-mixed low-plankton-biomass zone, and area of high wild-farmed fish interactions.

## Program Objectives

1) Determine migration timing and pathways; 

2) Migration habitat mapping - oceanographic conditions along the migration route;

3) Understand the dynamics of the plankton food-webs that underpin juvenile salmon growth and
health;

4) Understand parasite and pathogen infection dynamics and their impact on juvenile salmon growth and
health.

## Key Parameters Reported
* Catch Statistics
* Parasite Loads
* Sockeye Length and Weight
* Oceanographic Conditions

![Salmon sampling locations in the Discovery Islands and Johnstone Strait in 2017 (yellow circles).](./figs/map_2017.pdf)

The following plots are subject to change as the underlying data are preliminary and subject to further quality assurance. 

We are endeavouring to provide useful information for the entire salmon research community. As such we welcome any feedback. Please direct questions or comments to Brian Hunt (B.Hunt@oceans.ubc.ca) and/or Brett Johnson (Brett.Johnson@hakai.org). 

__Report prepared by:__ Brett Johnson, Carly Janusson, Julian Gan, and Brian Hunt  
__Updated:__ `r Sys.Date()`  



## Catch Statistics
### Cumulative Abundance of all Species

```{r All Species Cumulative Abundance, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "The cumulative abundance of fish captured in the Discovery Islands and Johnstone Strait in 2017."}
# This calculates cumulative abundance, regardless of region

cum_abund <- survey_seines %>%
                select(region, survey_date, so_total, pi_total, cu_total, co_total, he_total, ck_total) %>%
                group_by(region, survey_date) %>% 
                summarise(daily_so = mean(so_total), 
                          daily_pi = mean(pi_total),
                          daily_cu = mean(cu_total),
                          daily_co = mean(co_total),
                          daily_he = mean(he_total),
                          daily_ck = mean(ck_total)) %>% 
                ungroup()

js_cum_abund <- cum_abund %>% 
                filter(region == "JS") %>% 
                transmute(survey_date = survey_date, region = region,
                              so.cum.abund = cumsum(daily_so), 
                              pi.cum.abund = cumsum(daily_pi),
                              cu.cum.abund = cumsum(daily_cu),
                              co.cum.abund = cumsum(daily_co),
                              he.cum.abund = cumsum(daily_he),
                              ck.cum.abund = cumsum(daily_ck)
                              ) %>% 
                 gather(so.cum.abund, pi.cum.abund, cu.cum.abund,
                           co.cum.abund, he.cum.abund, ck.cum.abund, key = "species", value = "cum.abund") %>% 
                ungroup()

di_cum_abund <- cum_abund %>% 
                filter(region == "DI") %>% 
                transmute(survey_date = survey_date, region = region,
                              so.cum.abund = cumsum(daily_so), 
                              pi.cum.abund = cumsum(daily_pi),
                              cu.cum.abund = cumsum(daily_cu),
                              co.cum.abund = cumsum(daily_co),
                              he.cum.abund = cumsum(daily_he),
                              ck.cum.abund = cumsum(daily_ck)
                              ) %>% 
                 gather(so.cum.abund, pi.cum.abund, cu.cum.abund,
                           co.cum.abund, he.cum.abund, ck.cum.abund, key = "species", value = "cum.abund")  

cum_abund <- rbind(di_cum_abund,js_cum_abund)

labels <- c(DI = "Discovery Islands", JS = "Johnstone Strait")

cum_abund_plot <- ggplot(data = cum_abund, mapping = aes(x = survey_date, y = cum.abund)) +
        geom_point(mapping = aes(colour= species)) +
        geom_line(mapping = aes(colour = species)) +
        ylab("Cumulative abundance") + xlab("Date") + 
        facet_grid(region ~., labeller=labeller(region = labels))+
        scale_colour_discrete(name = "",
                        breaks=c("co.cum.abund","cu.cum.abund", "he.cum.abund", "pi.cum.abund", "so.cum.abund",
                                 "ck.cum.abund"),
                        labels=c("Coho", "Chum", "Herring", "Pink", "Sockeye", "Chinook"))+
        theme(legend.justification=c(1,0),
                legend.background = element_rect(fill="white")) +  
        theme(legend.text = element_text(colour="black", size = 12))+ 
        theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))+
        theme(legend.justification=c(1,0), legend.position=c(.3,.6),
             legend.background = element_rect(fill="white")) 
cum_abund_plot 
ggsave(here("In-season Reports", "2018_in_season_report", "figs", "all_spp_cumulative_abundance.png"))

```

### Cumulative Abundance of Sockeye by Region
```{r Sockeye Cumulative Abundance, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The cumulative abundance of sockeye captured in the Discovery Islands and Johnstone Strait in 2017."}
# Create new columns for cumulative sums of each species captured
# Average multiple seines conducted in the same region on the same day

# This summarises and averages cpue grouped by region and sampling day
cum_abund_by_region <- survey_seines %>% 
                select(survey_date, region, so_total, pi_total,
                       cu_total, co_total, he_total) %>%
                drop_na() %>% 
                group_by(region, survey_date) %>% 
                summarise(daily_so = mean(so_total), 
                          daily_pi = mean(pi_total),
                          daily_cu = mean(cu_total),
                          daily_co = mean(co_total),
                          daily_he = mean(he_total)
                )

# This replaces cpue for each day and each region with the cumulative sum for each species, and then tidys the data so that each row is only one observation
cum_abund_by_region <- cum_abund_by_region %>% 
                    transmute(survey_date = survey_date,
                              so_cum_abund = cumsum(daily_so), 
                              pi_cum_abund = cumsum(daily_pi),
                              cu_cum_abund = cumsum(daily_cu),
                              co_cum_abund = cumsum(daily_co),
                              he_cum_abund = cumsum(daily_he)
                              ) %>% 
                    gather(so_cum_abund, pi_cum_abund, cu_cum_abund,
                           co_cum_abund, he_cum_abund, key = "species", value = "cum_abund")        

# This plots cumulative abundnace of sockeye grouped by region

so_cum_abund_plot <- ggplot(data = filter(cum_abund_by_region, species == "so_cum_abund"),
        mapping = aes(x = survey_date, y = cum_abund)) +
        geom_point(mapping = aes(colour= region)) +
        geom_line(mapping = aes(colour = region)) +
        ylab("Sockeye cumulatve abundance") + xlab("Date") +
        scale_colour_discrete(name = "",
                        breaks=c("DI","JS"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
        theme(legend.justification=c(1,0),legend.background = element_rect(fill="white")) +  
                theme(legend.text = element_text(colour="black", size = 12)) +                         theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold"))+
        theme(legend.justification=c(1,0), legend.position=c(.4,.8),
             legend.background = element_rect(fill="white")) 
so_cum_abund_plot
```

### Sockeye Catch Per Unit Effort

```{r Sockeye CPUE, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="Catch per unit effort of juvenile sockeye salmon in 2017 averaged over one week periods for each region."}

avg_school_size <- survey_seines %>% 
  select(year, region, sampling_week, so_total) %>% 
  group_by(year, region, sampling_week) %>% 
  summarise(mean = mean(so_total, na.rm = T), se = (sd(so_total) / sqrt(n())))

so_abund_timing <- ggplot(data = avg_school_size, aes(x = sampling_week, y = mean, colour = region, group = region))+
  geom_line(size = 1)+
  geom_point(position = position_dodge(width = 0.05))+
  xlab("Date") +
  ylab("Sockeye CPUE") +
  coord_cartesian(xlim = 1:11) +
  scale_colour_discrete(name = "",
                        breaks=c("DI","JS"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
  theme(legend.justification=c(1,0), legend.position=c(.8,.8),
        legend.background = element_rect(fill="white")) + 
  theme(legend.text = element_text(colour="black", size = 12)) +                           theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) +
  geom_point(size = 1.75, position = position_dodge(width = 0.1)) +
  xlab("Date") +
  ylab("Sockeye abundance") +
  theme(legend.title = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
so_abund_timing
```

\newpage

## Parasite Loads 

### Definitions[^1] 

_Prevalence_: Number of individuals of a host species infected with a particular parasite species ÷ Number of hosts examined. 

_Mean Infection Intensity_: Total number of individuals
of a particular parasite species
in a sample of a host species ÷ Number
of infected individuals of the host
species in the sample (= Mean number
of individuals of a particular parasite
species per infected host in a sample). 

_Abundance_: The total number of individuals of a particular parasite species in a sample of hosts ÷ Total number of individuals of the host species in the sample.

[^1]: Margolis, L., Esch, G.W., Holmes, J.C., Kuris, A.M. and Schad, G.A. (1982). The use of ecological terms in parasitology: report of an ad hoc committee of the American Society of Parasitologists. J. Parasitol. 68:131–133.

### Sea Lice Prevalence


```{r Sealice setup, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE}

# Group fish by region and by sampling week to calculate prevalence of sea-lice
sea_lice_2018_summary <- fish_and_sealice_field_data %>%
  filter(species %in% c("SO", "PI", "CU")) %>% 
        mutate(total_lice = cal_cope + lep_cope + chal_a +
                        chal_b + cm + cpaf + caf + cgf + lpam + lpaf + lam + laf + lgf
                        + unid_cope + unid_chal,
               copepodid = cal_cope + lep_cope + unid_cope,
               chalimus = chal_a + chal_b + unid_chal,
               motile = cm + cpaf + caf + cgf + lpam + lpaf + lam + laf + lgf,
               motile_caligus = cm + cpaf + caf + cgf,
               motile_lep = lpam + lpaf + lam + laf + lgf
        )
```

```{r Lice Prevalence, fig.cap= "The proportion of juvenile chum, pink and sockeye that had at least one motile sea louse of either _Lepeoptheirus salmonis_ and _Caligus clemensi_ in the Discovery Islands and Johnstone Strait in 2017."}
# Summarize data to calcuate the average prevalence by region and sampling week with SD
motile_sea_lice_2018_prevalence <- sea_lice_2018_summary %>%
                group_by(region, species, sampling_week) %>%
                summarize(prevalence = mean(motile, na.rm = T))

labels <- c(CU = "Chum", PI = "Pink", SO = "Sockeye")
                

motile_sea_lice_2018_prevalence_plot <- ggplot(data = motile_sea_lice_2018_prevalence, aes(x = sampling_week, y = prevalence, colour = region))+
  geom_point(position = position_dodge(0.05))+
  geom_line()+
  ylab("Prevalence")+
  xlab("Date")+
  theme(legend.position="none") +
  theme(legend.text = element_text(colour="black", size = 12)) + 
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))+
  coord_cartesian(y= 0:1)+
  facet_grid(region~species, scales = "free_y", labeller=labeller(species = labels)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

motile_sea_lice_2018_prevalence_plot
```

\newpage

### All Sea-lice Life-stages Infection Abundance on Sockeye

```{r All stages Lice Abundance, fig.cap= "The abundance ± SE of three developmental stages of both _Lepeoptheirus salmonis_ and _Caligus clemensi_ sea lice per juvenile sockeye salmon in 2018."}

sea_lice_2018_avg <- sea_lice_2018_summary %>%
  filter(species == "SO") %>% 
                select(region, sampling_week, copepodid, chalimus, motile) %>% 
                group_by(region, sampling_week) %>%
                summarise(
                        cope    = mean(copepodid, na.rm = T),
                        chal    = mean(chalimus, na.rm = T),
                        mot     = mean(motile, na.rm =T)) %>%
                gather(cope, chal, mot, key = "life_stage", value = "abundance") 

sea_lice_2018_se <- sea_lice_2018_summary %>% 
  filter(species == "SO") %>% 
                select(region, sampling_week, copepodid, chalimus, motile) %>% 
                        group_by(region, sampling_week) %>%
                        summarise(
                                cope = sd(copepodid, na.rm = T)/sqrt(n()),  
                                chal = sd(chalimus, na.rm = T)/sqrt(n()),  
                                mot  = sd(motile, na.rm = T )/sqrt(n())) %>% 
                        gather(cope, chal, mot, key = life.stage, value = "se")

sea_lice_2018_avg$se <- sea_lice_2018_se$se

sea_lice_2018_avg$sampling_week <- as.factor(sea_lice_2018_avg$sampling_week)
stages <- c("cope", "chal", "mot")
sea_lice_2018_avg$life_stage <- factor(sea_lice_2018_avg$life_stage, levels = c("cope", "chal", "mot"))

#Plot abundnace

labels <- c('DI' = "Discovery Islands", 'JS' = "Johnstone Strait")


sea_lice_2018_abundance_plot <- ggplot(data = sea_lice_2018_avg, aes(x = sampling_week, y = abundance, fill = life_stage))+
  geom_bar(position = position_dodge(), stat= "identity")+
  geom_errorbar(aes(ymin = abundance-se, ymax = abundance+se), 
                width = .2,
                position = position_dodge(.9))+
  facet_grid(region ~., labeller = as_labeller(labels))+ 
  ylab("Abundance")+
  xlab("Date")+
  scale_fill_discrete(name = "",
                      breaks=c("cope", "chal", "mot"),
                      labels=c("Copepodid", "Chalimus", "Motile")) +
  theme(legend.text = element_text(colour="black", size = 12)) +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=12,face="bold"))
sea_lice_2018_abundance_plot
```


### Motile Abundance for Chum, Pink, and Sockeye

```{r Motile Caligus and Lep abundance on chum. pink, and sockeye , fig.cap = "The abundance  ± SE of __motile__ _Lepeoptheirus salmonis_ and _Caligus clemensi_ sea lice combined infecting juvenile chum, pink and sockeye salmon in the Discovery Islands and Johnstone Strait in 2018."}

sea_lice_2018_mot <- sea_lice_2018_summary %>% 
                select(region, species, sampling_week, motile_caligus, motile_lep) %>% 
                group_by(region, species, sampling_week) %>%
                summarise(cal    = mean(motile_caligus, na.rm = T),
                          lep    = mean(motile_lep, na.rm = T)) %>%
                gather(cal, lep, key = "lice_species", value = "abundance") 

sea_lice_2018_mot_se <- sea_lice_2018_summary %>% 
                select(region, species, sampling_week, motile_caligus, motile_lep) %>% 
                        group_by(region, species, sampling_week) %>%
                        summarise(
                                cal = sd(motile_caligus, na.rm = T)/sqrt(n()),  
                                lep = sd(motile_lep, na.rm = T)/sqrt(n())) %>% 
                        gather(cal, lep, key = lice_species, value = "se")

sea_lice_2018_mot$se <- sea_lice_2018_mot_se$se

sea_lice_2018_mot$sampling_week <- as.factor(sea_lice_2018_mot$sampling_week)

motile_abundance_plot <- ggplot(sea_lice_2018_mot, aes(x = sampling_week, y = abundance, colour = lice_species, group = lice_species))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = abundance - se, ymax = abundance + se, width = 0.1))+
  facet_grid(region~., labeller = as_labeller(labels))+
  xlab("Date")+
  ylab("Infection Abundance")+
  scale_colour_discrete(name = "",
                        breaks=c("cal", "lep"),
                        labels=c("Caligus clemensi", "Lepeioptheirus salmonis"))+ 
  theme(legend.text = element_text(colour="black", size = 12, face = "italic")) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=12,face="bold")) +
  facet_grid(region~species)+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
        
motile_abundance_plot

```

\newpage

### Combined Motile _Lep._ and _Cal._ Intensity for Chum, Pink, and Sockeye

```{r Motile infection intensity, fig.cap = "The mean infection intensity of __motile__ _Lepeoptheirus salmonis_ and  _Caligus clemensi_ sea lice combined on juvenile sockeye salmon in the Discovery Islands and Johnstone Strait in 2018."}

sea_lice_2018_intensity <- sea_lice_2018_summary %>% 
  filter(motile > 0) %>% 
  select(region, species, sampling_week, motile) %>% 
  group_by(region, species, sampling_week) %>%
  summarise(intensity =  mean(motile, na.rm = T)) 

sea_lice_2018_intensity_se <- sea_lice_2018_summary %>%
  filter(motile > 0) %>% 
  select(region, species, sampling_week, motile) %>% 
  group_by(region, species, sampling_week) %>%
  summarise(se = sd(motile, na.rm = T)/sqrt(n()))

sea_lice_2018_intensity$se <- sea_lice_2018_intensity_se$se

spp_labels <- c(CU = "Chum", PI = "Pink", SO = "Sockeye", DI = "Discovery Islands", 
                JS = "Johnstone Strait")
                
sea_lice_intensity_plot <- ggplot(sea_lice_2018_intensity,
                                  aes(x = sampling_week,
                                      y = intensity, group = region))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = intensity - se, ymax = intensity + se, width = 0.1))+
  facet_grid(region~species, labeller = as_labeller(spp_labels))+
  xlab("Date")+
  ylab("Mean Infection Intensity")+
  theme(legend.justification=c(1,0), legend.position=c(.4,.3),
        legend.background = element_rect(fill="white")) +  
  theme(legend.text = element_text(colour="black", size = 12,
                                   face = "italic")) + 
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

        
sea_lice_intensity_plot
```

\newpage

#### Motile _Caligus clemensi_ Infection Intensity 
```{r Lice cal intensity, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The mean infection intensity of __motile__ _Caligus clemensi_ sea lice per juvenile sockeye salmon infected with one or more motile _Caligus clemensi_."}

sea_lice_2018_cal_mot_intensity <- sea_lice_2018_summary %>% 
  filter(motile_caligus > 0) %>% 
  select(region, species, sampling_week, motile_caligus) %>% 
  group_by(region, species, sampling_week) %>%
  summarise(intensity =  mean(motile_caligus, na.rm = T))

sea_lice_2018_cal_mot_intens_se <- sea_lice_2018_summary %>%
  filter(motile_caligus > 0) %>% 
  select(region, species, sampling_week, motile_caligus) %>% 
  group_by(region, species, sampling_week) %>%
  summarise(se = sd(motile_caligus, na.rm = T)/sqrt(n()))

sea_lice_2018_cal_mot_intensity$se <- sea_lice_2018_cal_mot_intens_se$se

cal_mot_intensity_plot <- ggplot(sea_lice_2018_cal_mot_intensity, 
                                 aes(x = sampling_week, y = intensity, group = region))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = intensity - se, ymax = intensity + se, width = 0.1))+
  facet_grid(region~species, labeller = as_labeller(spp_labels))+
  xlab("Date")+
  ylab("Mean Infection Intensity")+
  theme(legend.justification=c(1,0), legend.position=c(.4,.3),
        legend.background = element_rect(fill="white")) +  
  theme(legend.text = element_text(colour="black", size = 12, face = "italic")) +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=12,face="bold")) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))


cal_mot_intensity_plot


```

\newpage

#### Motile _Lepeoptheirus salmonis_ Infection Intensity

```{r Lice lep intensity, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The mean intensity of __motile__ _Lepeoptheirus salmonis_ sea lice per juvenile sockeye salmon infected with one or more motile _Lepeoptheirus salmonis_."}

sea_lice_2018_lep_mot_intensity <- sea_lice_2018_summary %>% 
  filter(motile_lep > 0) %>% 
  select(region, species, sampling_week, motile_lep) %>% 
  group_by(region, species, sampling_week) %>%
  summarise(intensity =  mean(motile_lep, na.rm = T))

sea_lice_2018_lep_mot_intens_se <- sea_lice_2018_summary %>%
  filter(motile_lep > 0) %>% 
  select(region, species, sampling_week, motile_lep) %>% 
  group_by(region, species, sampling_week) %>%
  summarise(se = sd(motile_lep, na.rm = T)/sqrt(n()))

sea_lice_2018_lep_mot_intensity$se <- sea_lice_2018_lep_mot_intens_se$se

lep_mot_intensity_plot <- ggplot(sea_lice_2018_lep_mot_intensity,
                                 aes(x = sampling_week, y = intensity, group = region))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = intensity - se, ymax = intensity + se, width = 0.1))+
  facet_grid(region~species, labeller = as_labeller(spp_labels))+
  xlab("Date")+
  ylab("Mean Infection Intensity")+
  theme(legend.justification=c(1,0), legend.position=c(.4,.3),
        legend.background = element_rect(fill="white")) +  
  theme(legend.text = element_text(colour="black", size = 12, face = "italic")) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=12,face="bold"))  +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))


lep_mot_intensity_plot

```

\newpage

## Fish Length and Weight
### Sockeye Length
```{r Length Histogram, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "Length frequency histogram of juvenile sockeye in the Discovery Islands and Johnstone Strait in 2017."}

length_histo <- fish_and_sealice_field_data %>% 
  filter(species %in% c("SO", "PI", "CU")) %>% 
  ggplot(aes(x = sampling_week, y = fork_length, fill = species)) +
  geom_boxplot()+
  ylab("Fork Length (mm)")+
  ylab("Date")+
  theme(legend.text = element_text(colour="black", size = 12)) + 
  theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold")) +
  facet_grid(region~.)
length_histo
```

### Sockeye Weight
```{r Weight Histogram, echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "Weight frequency histogram of juvenile sockeye salmon in the Discovery Islands and Johnstone Strait in 2017."}

weight_histo <- fish_and_sealice_field_data %>% 
  filter(species %in% c("SO", "PI", "CU")) %>% 
  ggplot(aes(x = sampling_week, y = weight, fill = species)) +
  geom_boxplot() +
  ylab("Weight (g)")+
  xlab("Sampling Week")+
  theme(legend.text = element_text(colour="black", size = 12)) + 
  theme(axis.text=element_text(size=12),
                axis.title=element_text(size=12,face="bold")) +
  facet_grid(region~.)
weight_histo
```



```{r Sea Surface Temp, include = FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap= "Sea surface temperature in the Discovery Islands and Johnstone Strait averaged by date and region in 2017."}

ysi_data <- ysi_data %>% 
                group_by(Survey, Date) %>% 
                summarise(avg.temp = mean(temp))

sst_plot <- ggplot(ysi_data, aes(x = Date, y = avg.temp, colour = Survey, group = Survey)) +
        geom_point() +
        geom_line() +
        theme(legend.text = element_text(colour="black", size = 12),
              axis.text=element_text(size=12),axis.title=element_text(size=12,face="bold")) +
         scale_color_discrete(name = "",
                        breaks=c("DISOCKEYE", "JSSOCKEYE"),
                        labels=c("Discovery Islands", "Johnstone Strait"))+
        ylab("Average temperature (ºC)")+
        theme(legend.justification=c(1,0), legend.position=c(.4,.8),
             legend.background = element_rect(fill="white")) 

sst_plot
ggsave("./final_figures/sst_plot.png")


```