---
title: "Hakai Institute Juvenile Salmon Program Report"
output:
  rmarkdown::pdf_document:
    
    fig_caption: yes
    includes:
      in_header: figure_opts.tex
    latex_engine: xelatex
sansfont: Times New Roman
fontsize: 12pt

header-includes:
- \usepackage{booktabs}
- \usepackage{sectsty} \sectionfont{\centering \emph}
      
---

\begin{center}
\large
— Hakai Institute Juvenile Salmon Program —
\end{center}

```{r, include = FALSE}
library(hakaisalmon)
library(tidyverse)
```

# Highlighted Outputs

## Conference presentations and posters

__Johnson, B.T.__, C. Neville, B.P.V. Hunt. 2018. *Fine scale migration dynamics of juvenile sockeye in the Discovery Islands, B.C.* Salmon Ocean Ecology Meeting. Newport, Oregon. *Oral* 

__Hunt, B.P.V.__ 2018. *Integrated biogeochemical approaches to full salmon life history analysis.* Salmon Ocean Ecology Meeting. Newport, Oregon. *Oral*

__James, S.__ 2018. *Characterizing the diets of juvenile Fraser River sockeye salmon across ocean regimes in coastal British Columbia*. Salmon Ocean Ecology Meeting. Newport, Oregon. *Oral*

__Hunt, B.P.V.__, B.T. Johnson. 2017 *[Juvenile Salmon Program update; foraging conditions, migration dynamics, and growth](https://speakerdeck.com/brettjohnson/psf-ssmsp-2017).* Pacific Salmon Foundation Salish Sea Marine Survival Project international conference. Richmond, BC, Canada. *Oral*

__Johnson, B.T.__, J.C.L. Gan, C.V. Janusson, B.P.V. Hunt. 2017. *Hakai Institute Juvenile Salmon Program 2015--2017 Time Series Poster.* Poster presentation at the Pacific Salmon Foundation Salish Sea Marine Survival Project juvenile salmon workgroup. Nanaimo, BC, Canada. *Poster*

__Johnson, B.T.__, J.C.L. Gan, C.V. Janusson, B.P.V. Hunt. 2017. *Hakai Institute Juvenile Salmon Program 2015--2016 Time Series Poster*. Poster presentation at Fisheries and Oceans Canada State of the Pacific Ocean meeting. Sidney, BC, Canada. *Poster*

## Publications

### In preparation

__Johnson, B.T.__, J.C.L. Gan, C.V. Janusson, B.P.V. Hunt. 2018. *Hakai Institute Juvenile Salmon Program migration monitoring 2015 -- 2017 time series* In preparation for the North Pacific Anadromous Fisheries Commission document reports.

__Johnson, B.T.__, C. Neville, B.P.V. Hunt. 2018. *Fine scale migration dynamics of juvenile sockeye salmon in the Discovery Islands, B.C.* In preparation for Marine and Coastal Fisheries journal.


## Data

* Salmon program data restructuring for Hakai EIMS database creation
* [Citable data package](http://dx.doi.org/10.21966/1.566666) produced for collaborators
* [R package](https://github.com/HakaiInstitute/hakaisalmon) produced for program data and custom functions for summarizing program data
* Salmon program data now in the Hakai Data Portal

# Lab and Analysis Progress

## Fish dissected and samples created
```{r include = FALSE}
n_fish_after_2017 <- as.numeric(survey_seines_fish %>%
  filter(date_processed > "2017-08-01") %>% 
  select(ufn, date_processed) %>% 
  nrow())

library(googlesheets)
sample_inventory_workbook <- gs_title("SEMSP Current Sample Inventory")

rna_metadata <- gs_read(sample_inventory_workbook, ws = "rna_metadata")
fa_metadata <- gs_read(sample_inventory_workbook, ws = "da_metadata")



n_samples_dissected <- rbind(
  
n_fish <- as.numeric((survey_seines_fish) %>%
  select(ufn, date_processed) %>% 
  drop_na(date_processed) %>% 
  nrow())


```

* Since the 2017 field season finished after August 1 2017, `r n_fish_after_2017` were dissected
* Since the 2017 field season finished after August 1 2017, 
* Since the program began exactly `r n_fish` have been dissected.

## Samples processed

## Inventory

# Next Steps

## Field season

## Acoustic tagging
